\Title

### 2015-11-02 manuscript.tex
Started CV for regul param section

\subsection{Determination of hyper-parameters}

There are three hyper-parameters that control the inversion results:
(1) the regularization parameter $\mu$
(2) the depth of the Moho of the reference ellipsoid
(3) the density-contrast between the

>>>>

\subsection{Estimating the regularization parameter}

The regularization parameter $\mu$ controls how much smoothness is applied to
the inversion result.
An optimal value of $\mu$ will stabilize and smooth the solution while not
compromising the fit to the observed data.
Two widely used methods to estimate an optimal $\mu$ are
the L-curve criterion and cross-validation \citep{hansen1992}.
Here, we will adopt the hold-out method of cross-validation \citep{kim2009}.
\todo{Not the best reference}
The hold-out method consists of splitting the observed data set into two
independent parts:
a training set $\mathbf{d}^o_{inv}$
and a testing set $\mathbf{d}^o_{test}$.
The training set is used in the inversion
while the testing set is kept back
and used to judge the quality of the chosen value of $\mu$.
For a value of the regularization parameter $\mu_k$,
the training set is inverted using $\mu_k$
to obtain an estimate $\mathbf{\hat{p}}^k$.
This estimate is used to calculate predicted data
on the same points as the testing set
via forward modeling
($\mathbf{d}_{test}^k = \mathbf{f}(\mathbf{\hat{p}}^k$)).
The metric chosen to evaluate $\mu_k$ is
the mean square error (MSE) of the misfit
between the observed and predicted testing data sets,

\begin{equation}
    MSE_k = \dfrac{\|\mathbf{d}^o_{test} - \mathbf{d}^k_{test}\|^2}{N_{test}},
    \label{eq:msemu}
\end{equation}

\noindent
in which $N_{test}$ is the number of data in the testing set.
The optimal value of $\mu$ will be the one that minimizes the MSE,
i.e. the one that best predicts the testing data.
We emphasize that the inversion is performed only on the training data set.

The algorithm for the hold-out cross-validation is summarized as follows:

\begin{enumerate}
    \item Divide the observed data into
        the training ($\mathbf{d}^o_{inv}$)
        and testing ($\mathbf{d}^o_{test}$) sets.
    \item For each $\mu_k \in [\mu_1, \mu_2, \ldots, \mu_{N_{\mu}}]$:
    \begin{enumerate}
        \item Estimate $\mathbf{\hat{p}}^k$ by inverting the training set
            $\mathbf{d}^o_{inv}$.
        \item Use $\mathbf{\hat{p}}^k$ to calculate the predicted testing set
            $\mathbf{d}^k_{test}$.
        \item Calculate the mean square error $MSE_k$ using Eq.~\ref{eq:msemu}.
    \end{enumerate}
    \item The final solution is the $\mathbf{\hat{p}}^k$ corresponding to the
        smallest $MSE_k$.
\end{enumerate}

Bott's method requires the same number of observed data ($N$)
and model parameters ($M$).
Limited ways to separate the training and testing data sets.
Data and model must be on a regular grid.
Cannot randomly separate.
Use a dense data grid.
Take for the training set a sub grid with double the original grid spacing.
Every other point is included in the testing data set.
The testing data set will have more points than training data set.
One can generate observed data on a grid with half of the desired grid spacing.
This is easy for data generated from spherical harmonic models.

\subsection{Estimating $z_{ref}$ and $\Delta\rho$}
